### 2024-01-04 sections/2-methods.tex
incorporate some of Carl's suggestions

Based on our asymptotic complexity analyses, we expect CAKES to perform well on datasets with low LFD, and forS performance to scale sub-linearly with the cardinality of the dataset.
To test this hypothesis, we use some datasets from the ANN-benchmarks suite~\cite{aumuller2020ann} and synthetically augment them to generate similar datasets with exponentially larger cardinalities.
We do the same with a large random dataset of uniformly distributed points in a hypercube.
We then compare the performance of CAKES to that of other algorithms on the original datasets and the synthetically augmented datasets.

>>>>

Based on our asymptotic complexity analyses, we expect CAKES to perform well on datasets with low LFD, and for its performance to scale sub-linearly with the cardinality of the dataset.
To test this hypothesis, we use some datasets from the ANN-benchmarks suite~\cite{aumuller2020ann} and synthetically augment them to generate similar datasets with exponentially larger cardinalities.
We do the same with a large random dataset of uniformly distributed points in a hypercube.
We then compare the performance of CAKES to that of other algorithms on the original datasets and the synthetically augmented datasets.

### 2024-01-04 sections/4-results.tex
incorporate some of Carl's suggestions

Figure~\ref{fig:results:lfd-plots} the trends in LFD for (the non-augmented versions of) Fashion-Mnist, Glove-25, Sift, Random, Silva 18S, and RadioML.
The horizontal axis denotes the depth in the cluster tree, and the vertical axis denotes the LFD (as calculated by Equation~\ref{eq:methods:lfd-simplified}) of clusters at that depth.
We plot lines for the 5$^{th}$, 25$^{th}$, 50th, 75$^{th}$ and 95$^{th}$ percentiles of LFD, as well as the minimum and maximum LFD at each depth.
In order to have the plots to best reflect the distribution of LFDs across the entire \textit{dataset}, we compute percentiles counting each cluster as many times as its cardinality.
In other words, if, for some dataset, the 95$^{th}$ percentile of LFD at depth 40 is 3, this means that 95\% of the total points in clusters at depth 40 belong to clusters whose LFD is at most 3.

@@

Relative to the other datasets, RadioML, as displayed in Figure~\ref{fig:results:radioml-lfd}, exhibits high LFD.
Notably however, for the first approximately 15 depths, the 95$^{th}$ percentile and median LFD are very close to 0.
Both percentiles increase sharply after depth 20, nearly reaching 16.
LFD remains high even as depth increases, with the 95$^{th}$ percentile fluctuating between about 6 and 15 for depths about 20-40.
It then spikes up again to about 10 at around depth 45 before decreasing linearly to 1 at depth 60.
The median LFD follows a similar pattern of peaks and troughs, fluctuating between about 3 and 15 for depths 20-40, spiking at about depth 50 to 5, and then decreasing approximately linearly to 1 at depth 60.

@@

The horizontal axis in each figure shows the cardinality of the augmented dataset with synthetic points (see Section \ref{sec:methods:synthetic-data}).
The left-most point on each line is at the cardinality of the original dataset without any synthetic augmentation..
The vertical axis denotes throughput in queries per second.
Both axes are on a logarithmic scale.
In this section, we report results only for $k$-NN search with $k = 10$, but similar plots for $k = 100$ can be found in the Supplement.
For HNSW and ANNOY, we report the recall for each measurement in the plots. For algorithms which exhibit recall greater than $0.9995$, we do not report the recall in the plots, but we do report it in the tables below.

>>>>

Figure~\ref{fig:results:lfd-plots} illustrates the trends in LFD for (the non-augmented versions of) Fashion-Mnist, Glove-25, Sift, Random, Silva 18S, and RadioML.
The horizontal axis denotes the depth in the cluster tree, and the vertical axis denotes the LFD (as calculated by Equation~\ref{eq:methods:lfd-simplified}) of clusters at that depth.
We plot lines for the 5$^{th}$, 25$^{th}$, 50th, 75$^{th}$ and 95$^{th}$ percentiles of LFD, as well as the minimum and maximum LFD at each depth.
In order to have the plots to best reflect the distribution of LFDs across the entire \textit{dataset}, we compute percentiles counting each cluster as many times as its cardinality.
In other words, if, for some dataset, the 95$^{th}$ percentile of LFD at depth 40 is 3, this means that 95\% of the total points in clusters at depth 40 belong to clusters whose LFD is at most 3.

@@

Relative to the other datasets, RadioML, as displayed in Figure~\ref{fig:results:radioml-lfd}, exhibits high LFD.
Notably, however, for the first approximately 15 depths, the 95$^{th}$ percentile and median LFD are very close to 0.
Both percentiles increase sharply after depth 20, nearly reaching 16.
LFD remains high even as depth increases, with the 95$^{th}$ percentile fluctuating between about 6 and 15 for depths about 20-40.
It then spikes up again to about 10 at around depth 45 before decreasing linearly to 1 at depth 60.
The median LFD follows a similar pattern of peaks and troughs, fluctuating between about 3 and 15 for depths 20-40, spiking at about depth 50 to 5, and then decreasing approximately linearly to 1 at depth 60.

@@

The horizontal axis in each figure shows the cardinality of the augmented dataset with synthetic points (see Section \ref{sec:methods:synthetic-data}).
The left-most point on each line is at the cardinality of the original dataset without any synthetic augmentation.
The vertical axis denotes throughput in queries per second.
Both axes are on a logarithmic scale.
In this section, we report results only for $k$-NN search with $k = 10$, but similar plots for $k = 100$ can be found in the Supplement.
For HNSW and ANNOY, we report the recall for each measurement in the plots. For algorithms which exhibit recall greater than $0.9995$, we do not report the recall in the plots, but we do report it in the tables below.
